Diffusion local times and the time until recombination

### 2015-10-16 notes/diffusion-local-times.Rmd
.

```{r doc_setup, include=FALSE}
fig.dim <- 5
knitr::opts_chunk$set(fig.width=2*fig.dim,fig.height=fig.dim,fig.align='center')
```

@@

>>>>

```{r doc_setup, include=FALSE}
fig.dim <- 5
knitr::opts_chunk$set(fig.width=2*fig.dim,fig.height=fig.dim,fig.align='center')
library(ReacTran)
library(deSolve)
```

@@

The exact solution
------------------

Let
$$
\zeta(x,t,r) = \P\{ T_r > t \} .
$$
Then the Kolmogorov forward equation tells us that $\zeta$ solves the following differential equation:
$$\begin{aligned}
    \frac{d}{dt} \zeta(x,t,r) 
    &= 
    \frac{\sigma^2}{2} \frac{d^2}{dx^2} \zeta(x,t,r) + \frac{d}{dx} \log(p(x)) \frac{d}{dx} \zeta(x,t,r)  - r f_H(x) \zeta(x,t,r)  \\
    \zeta(x,0,r) = 0 .
\end{aligned}$$

So, let's solve that, numerically.
We'll use the `ReacTran` library:
```{r solve_pde}
thegrid <- setup.grid.1D(x.up=-10, x.down=10, N = 1000)
driftfn <- setup.prop.1D(grid=thegrid, func=tanh_drift, s=s)
hetfn <- setup.prop.1D(grid=thegrid, func=tanh_het, s=s)
# ode.1D( )
```
